\section{User stories}

As a programmer I want to have access the entire project structure when using a code editor.

As a programmer I want clean seperation between branches and do not want to see changes to other branches when using a version control system.

As a programmer I want to be able to stage changes that I made to Git.

As a project manager I want to see who made a specific modification to a project in the version control system.

As a programmer I do not want to configure a second version control system when I already provided this information to Git.

As a programmer I do not want files covered by my .gitignore configuration to be shared with others.

As a programmer I want to be able to edit files with up to 4 people at a time. A file can have up to 30.000 characters.

\section{Scenarios}
Ih this section multiple scenarios are derived from the user stories.

\subsection{Scenario 1}
\label{sec:scenario1}
Person A and B are working on an Node.js Express project together. Person A is working on branch Ba, person B is working on Branch Bb.
Person A has edited the file /app.js (paths are described as absolute from the project root) as well as the file /routes/account.js on Ba.
Person B has edited the file /app.js as well as the file /routes/main.js on Bb.
Person A encounters unexpected behaviour of his code. He requests help from person B.
Neither persons A nor B want to commit their changes at this point.
Person B uses the VS Code Command Palette and chooses the option "Procurrently: Checkout Branch" and chooses branch Ba.
Person B now sees only the modifications in /app.js and /routes/accounts.js from branch Ba.
Upon discovering the problem in the sourcecode, person B modifies /routes/account.js to solve the problem.
Person A can see the the changes in real time.
Person B once again opens the VS Code Command Palette and chooses the option "Procurrently: Checkout Branch" and chooses branch Bb.
Person B now sees the modifications in /app.js and /routes/main.js on Branch Bb and can continue working on his task.

\subsection{Scenario 2}
Person A and B are working on an Node.js Express project together. Both of them are working on branch master in the /app.js file.
Person A is modifying and testing a new feature while person B is working on setting new HTTP caching headers for the Express app.
This is interfering with the test of person A. Person A opens the VS Code Command Palette and chooses the option "Procurrently: Toggle remote changes".
All the modifications of B are reverted in the documents of person A.
During that person B can still see the modifications of person A which helps person B to determine the correct caching headers for the different routes.
Person As laptop disconnects from the network. Therefore person B can no longer recieve real time updates from person A.
Person As laptop reboots unexpectedly. Once the laptop is booted up again, person A opens VS Code and can continue to work where he left off.
Person A now wants to know about the progress of person B and turns on remote changes. Person A can see all the changes of person B until person A disconnected from the network. Person A disables remote changes again and continues to work on his new feature.
Later on person Bs laptop reconnects to the network and person B can recieve all the modifications person B missed.
Once person A is happy with the implementation of the new feature, he wants to test the caching behaviour himself to make sure person B has understood his code correctly.
Person A opens the VS Code Command Palette and chooses the option "Procurrently: Toggle remote changes".
Person A now sees all the modifications of person B again including the modifications B made while person A had disabled the remote changes.